\textit{Red Oak}\\ Proactive Controller Generation for Algorithmic Policy

### 2015-05-11 draft.tex
..
reformatted code and examples

\title{\textit{Red Oak}: Proactive Policy Generation}
 \authorinfo{Ryan Beckett}{Princeton University}{rbeckett@princeton.edu}
 \authorinfo{Olivier Savary B\'{e}langer}{Princeton University}{olivierb@princeton.edu}

@@

This decision tree would, in turn, lead to the following set of prioritized symbolic rules. We call these symbolic rules because they represent constraints on the actual concrete rules. The concrete rules our system will install in the network depend on the current contents of the trusted connection relation. In particular, for each IP source that is trusted to communicate with an internal destination in the "conn" relation, we will get a concrete rule permitting this communication.
  \begin{lstlisting}
ipsrc in [0, 100] --> Sent to Controller
ipsrc in [101, 1000], (ipsrc,ipdst) in conn
                  --> Deliver
ipsrc in [101, 1000], (ipsrc,ipdst) not in conn
                  --> Drop
  \end{lstlisting}

After initialization (starting with no trusted connections), the concrete rules would be generated from the symbolic rules by having all relations be empty:
\begin{lstlisting}
ipsrc in [0, 100] ---> Sent to Controller  
ipsrc in [101, 1000] ---> Drop  
\end{lstlisting}

@@

  For example, a packing coming from \lstinline|ipsrc| 150 and \lstinline|ipdst| 10 would be matched by the second rule, and dropped on the switch.
Subsequently, on a packet with \lstinline|ipsrc| 10 and \lstinline|ipdst| 150, the first rules would be matched, evaluating the decision tree would add tuple $(10,150)$ to relation \lstinline|conn|, the packet would be forwarded according to the forwarding decision \lstinline|Deliver|, and the concrete rules would updated as follow:

\begin{lstlisting}
ipsrc in [0, 100] ---> Sent to Controller  
ipsrc = 150, ipdst = 10 ---> Deliver  
ipsrc in [101, 1000] ---> Drop  
\end{lstlisting}

@@

   \begin{figure}[ht]
\begin{lstlisting}
let f_cross (f_1) (f_2) pkt =
  let d_1 = f_1 pkt in
  let d_2 = f_2 pkt in
  Multicast (d_1,d_2)
\end{lstlisting}

@@

\begin{figure}[ht]
  \begin{lstlisting}
type packet

type field = IpSrc | IpDst

type range = (int*int) list

@@

type forwarding_decision =
	| Deliver
	| Drop
	| ForwardTo of int
	| Multicast of forwarding_decision
                      * forwarding_decision

val in_range: packet -> field -> range -> bool
\end{lstlisting}

@@

\begin{figure}[ht]
  \begin{lstlisting}
type relation = string

val add: packet -> field list -> relation
    -> unit

val remove: packet -> field list -> relation
    -> unit

val in_rel: packet -> field list -> relation
    -> bool
\end{lstlisting}

@@

\begin{figure}[ht]
  \begin{lstlisting}
val compile: (packet -> forwarding_decision)
    -> policy

val run: policy -> ((field * int) list) list
    -> unit

val print_policy: policy -> unit
  \end{lstlisting}

@@

For example, taking the following symbolic rules: 
  \begin{lstlisting}
ipsrc in [101, 1000], (ipsrc,ipdst) in conn
                  --> Deliver
ipsrc in [101, 1000], (ipsrc,ipdst) not in conn
                  --> Drop
  \end{lstlisting}
  and the relation ``conn'' as \lstinline| {(150,10), (200, 9), (8, 150)}|, we start by expanding the first rule to:
\begin{lstlisting}[mathescape]
ipsrc in ([101, 1000] $\cap$ 150), ipdst = 10
    --> Deliver
ipsrc in ([101, 1000] $\cap$ 200), ipdst = 9
    --> Deliver
ipsrc in ([101, 1000] $\cap$ 8), ipdst = 150
    --> Deliver
 \end{lstlisting}
which reduces to:
\begin{lstlisting}
ipsrc = 150, ipdst = 10
    --> Deliver
ipsrc = 200, ipdst = 9
    --> Deliver
 \end{lstlisting}
Note the omission of the third concrete rule, resulting from \lstinline|ipsrc| having an empty range. The second symbolic rule is then taken directly as concrete rule, with the packet in the relation having been matched by the previously generated concrete rule, resulting in:
\begin{lstlisting}
ipsrc = 150, ipdst = 10
    --> Deliver
ipsrc = 200, ipdst = 9
    --> Deliver  
ipsrc in [101, 1000]
    --> Drop
\end{lstlisting}

@@

From which the following symbolic rule would be generate:
\begin{lstlisting}
ipsrc in [0, 100], (ipdst, ipsrc) in conn
                  --> Deliver
ipsrc in [0, 100] --> Sent to Controller
ipsrc in [101, 1000], (ipsrc,ipdst) in conn
                  --> Deliver
ipsrc in [101, 1000], (ipsrc,ipdst) not in conn
                  --> Drop
\end{lstlisting}

With empty relation, the concrete rules would be the same as with the unoptimized decision tree. However, after seeing, for example, packet with \lstinline|ipsrc| 10 and \lstinline|ipdst| 150, the rules would be
\begin{lstlisting}
ipsrc = 10, ipdst = 150 ---> Deliver  
ipsrc in [0, 100] ---> Sent to Controller  
ipsrc = 150, ipdst = 10 ---> Deliver  
ipsrc in [101, 1000] ---> Drop  
\end{lstlisting}

>>>>

\title{\textit{Red Oak}\\ Proactive Controller Generation for Algorithmic Policy}
 \authorinfo{Ryan Beckett}{Princeton University}{rbeckett@princeton.edu}
 \authorinfo{Olivier Savary B\'{e}langer}{Princeton University}{olivierb@princeton.edu}

@@

This decision tree would, in turn, lead to the following set of prioritized symbolic rules. We call these symbolic rules because they represent constraints on the actual concrete rules. The concrete rules our system will install in the network depend on the current contents of the trusted connection relation. In particular, for each IP source that is trusted to communicate with an internal destination in the "conn" relation, we will get a concrete rule permitting this communication.
  \begin{lstlisting}[mathescape]
src $\in$ [0, 100] $\mapsto$ Controller
src $\in$ [101, 1000], (src,dst) $\in$ conn  $\mapsto$ Deliver
src $\in$ [101, 1000], (src,dst) $\notin$ conn $\mapsto$ Drop
  \end{lstlisting}

After initialization (starting with no trusted connections), the concrete rules would be generated from the symbolic rules by having all relations be empty:
\begin{lstlisting}[mathescape]
src $\in$ [0, 100] $\mapsto$ Controller  
src $\in$ [101, 1000] $\mapsto$ Drop  
\end{lstlisting}

@@

  For example, a packing coming from \lstinline|src| 150 and \lstinline|dst| 10 would be matched by the second rule, and dropped on the switch.
Subsequently, on a packet with \lstinline|src| 10 and \lstinline|dst| 150, the first rules would be matched, evaluating the decision tree would add tuple $(10,150)$ to relation \lstinline|conn|, the packet would be forwarded according to the forwarding decision \lstinline|Deliver|, and the concrete rules would updated as follow:

\begin{lstlisting}[mathescape]
src $\in$ [0, 100] $\mapsto$ Controller  
src = 150, dst = 10 $\mapsto$ Deliver  
src $\in$ [101, 1000] $\mapsto$ Drop  
\end{lstlisting}

@@

   \begin{figure}[ht]
\begin{lstlisting}
let f_cross (f1) (f2) pkt =
  let d1 = f1 pkt in
  let d2 = f2 pkt in
  Multicast (d1,d2)
\end{lstlisting}

@@

\begin{figure}[ht]
  \begin{lstlisting}[mathescape]
type pkt
type field = IpSrc | IpDst 
type fields = field list
type range = (int*int) list

type decision =
	| Deliver
	| Drop
	| ForwardTo of int
	| Multicast of decision * decision

@@

val in_range: pkt $\rightarrow$ field $\rightarrow$ range $\rightarrow$ bool
\end{lstlisting}

@@

\begin{figure}[ht]
  \begin{lstlisting}[mathescape]
type relation = string

val add: pkt $\rightarrow$ fields $\rightarrow$ relation $\rightarrow$ unit
val remove: pkt $\rightarrow$ fields $\rightarrow$ relation $\rightarrow$ unit
val in_rel: pkt $\rightarrow$ fields $\rightarrow$ relation $\rightarrow$ bool
\end{lstlisting}

@@

\begin{figure}[ht]
  \begin{lstlisting}[mathescape]
type examples =  ((field * int) list) list

val compile: (pkt $\rightarrow$ decision) $\rightarrow$ policy
val run: policy $\rightarrow$ examples $\rightarrow$ unit
  \end{lstlisting}

@@

For example, taking the following symbolic rules: 
  \begin{lstlisting}[mathescape]
src $\in$ [101, 1000], (src,dst) $\in$ conn $\mapsto$ Deliver
src $\in$ [101, 1000], (src,dst) $\notin$ conn $\mapsto$ Drop
  \end{lstlisting}
  and the relation ``conn'' as \lstinline| {(150,10), (200, 9), (8, 150)}|, we start by expanding the first rule to:
\begin{lstlisting}[mathescape]
src $\in$ ([101, 1000] $\cap$ 150), dst = 10 $\mapsto$ Deliver
src $\in$ ([101, 1000] $\cap$ 200), dst = 9 $\mapsto$ Deliver
src $\in$ ([101, 1000] $\cap$ 8), dst = 150 $\mapsto$ Deliver
 \end{lstlisting}
which reduces to:
\begin{lstlisting}[mathescape]
src = 150, dst = 10 $\mapsto$ Deliver
src = 200, dst = 9 $\mapsto$ Deliver
 \end{lstlisting}
Note the omission of the third concrete rule, resulting from \lstinline|ipsrc| having an empty range. The second symbolic rule is then taken directly as concrete rule, with the packet in the relation having been matched by the previously generated concrete rule, resulting in:
\begin{lstlisting}[mathescape]
src = 150, dst = 10 $\mapsto$ Deliver
src = 200, dst = 9 $\mapsto$ Deliver
src $\in$ [101, 1000] $\mapsto$ Drop
\end{lstlisting}

@@

From which the following symbolic rule would be generate:
\begin{lstlisting}[mathescape]
src $\in$ [0, 100], (dst, src) in conn $\mapsto$ Deliver
src $\in$ [0, 100] $\mapsto$ Controller
src $\in$ [101, 1000], (src,dst) $\in$ conn $\mapsto$ Deliver
src $\in$ [101, 1000], (src,dst) $\notin$ conn $\mapsto$ Drop
\end{lstlisting}

With empty relation, the concrete rules would be the same as with the unoptimized decision tree. However, after seeing, for example, packet with \lstinline|ipsrc| 10 and \lstinline|ipdst| 150, the rules would be
\begin{lstlisting}[mathescape]
src = 10, dst = 150 $\mapsto$ Deliver  
src $\in$ [0, 100] $\mapsto$ Controller  
src = 150, dst = 10 $\mapsto$ Deliver  
src $\in$ [101, 1000] $\mapsto$ Drop  
\end{lstlisting}
